---
title: | 
  | Assignment 4: Collaborating Together
  | Introduction to Applied Data Science
  | 2022-2023
author: |
  | Ying Ying Tsai
  | y.tsai1@students.uu.nl
  | https://github.com/yingying171
date: April 2023
urlcolor: purple
linkcolor: purple
output: 
  pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)
```

## Assignment 4: Collaborating Together

### Part 1: Contributing to another student's Github repository

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed.

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself.

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment.

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate.

**Question 1.1**: Fill in the **github username** of the class mate to whose repository you have contributed.

[Fill in here]

### Part 2: Analyzing various linear models

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package.

```{r, warning=FALSE, message=FALSE}
library(AER)
data(GrowthSW)

```

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

```{r}
library(modelsummary); library(tidyverse)

# write your code here
# Creating the treat variable based on revolutions
GrowthSW$treat <- ifelse(GrowthSW$revolutions > 0, "More than 0 revolutions", "0 revolutions")

# Summarizing the variables growth and rgdp60 by treat groups
summary_table <- datasummary(GrowthSW, 
                             var.labels = c(growth = "Growth", rgdp60 = "Real GDP 1960"),
                             by = "treat",
                             statistics = c("mean", "median", "sd", "min", "max"))

# Writing the resulting dataset to memory
write.csv(summary_table, file = "summary_table.csv", row.names = FALSE)
```

**Designated place**: type one or two sentences describing this table of a fellow student below. For example, comment on the mean and median growth of both groups. Then stage, commit and push it to their github repository.

### Part 3: Make a table summarizing reressions using modelsummary and kable

In question 2, we have seen that growth rates differ markedly between countries that experienced at least one revolution/episode of political stability and countries that did not.

**Question 3.1**: Try to make this more precise this by performing a t-test on the variable growth according to the group variable you have created in the previous question.

```{r}
# write t test here
t_test_result <- t.test(growth ~ treat, data = GrowthSW)

t_test_result

```

**Question 3.2**: What is the $p$-value of the test, and what does that mean? Write down your answer below.

We can also control for other factors by including them in a linear model, for example:

$$
\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \beta_2 \cdot \text{rgdp60}_i + \beta_3 \cdot \text{tradeshare}_i + \beta_4 \cdot \text{education}_i + \epsilon_i
$$

**Question 3.3**: What do you think the purpose of including the variable `rgdp60` is? Look at `?GrowthSW` to find out what the variables mean.

We now want to estimate a stepwise model. Stepwise means that we first estimate a univariate regression $\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \epsilon_i$, and in each subsequent model, we add one control variable.

**Question 3.4**: Write four models, titled `model1`, `model2`, `model3`, `model4` (using the `lm` function) to memory. Hint: you can also use the `update` function to add variables to an already existing specification.

```{r}
# Model 1: Univariate regression
model1 <- lm(growth ~ treat, data = GrowthSW)

# Model 2: Adding rgdp60 as a control variable to model 1
model2 <- update(model1, . ~ . + rgdp60)

# Model 3: Adding tradeshare as a control variable to model 2
model3 <- update(model2, . ~ . + tradeshare)

# Model 4: Adding education as a control variable to model 3
model4 <- update(model3, . ~ . + education)

save(model1, model2, model3, model4, file = "stepwise_models.RData")

```

Now, we put the models in a list, and see what `modelsummary` gives us:

```{r}

library(modelsummary)

# Putting the models in a list
model_list <- list(model1, model2, model3, model4)

# Applying modelsummary to the list of models
model_summary <- model_list |>
  modelsummary(stars = TRUE,
               statistics = c("rsq", "n"))
model_summary

```

**Question 3.5**: Edit the code chunk above to remove many statistics from the table, but keep only the number of observations $N$, and the $R^2$ statistic.

```{r}
# Loading the required packages
library(modelsummary)

# Putting the models in a list
model_list <- list(model1, model2, model3, model4)

# Applying modelsummary to the list of models
model_summary <- model_list |>
  modelsummary(stars = TRUE,
               statistics = c("n", "rsq"),
               output = "default")

# Printing the model summary
model_summary
```

**Question 3.6**: According to this analysis, what is the main driver of economic growth? Why?

**Question 3.7**: In the code chunk below, edit the table such that the cells (including standard errors) corresponding to the variable `treat` have a red background and white text. Make sure to load the `kableExtra` library beforehand.

```{r}
library(kableExtra)
library(modelsummary)

# Generating the model summary table
model_table <- list(model1, model2, model3, model4) |>
  modelsummary(stars = TRUE, gof_map = c("nobs", "r.squared"))

# Applying kableExtra functions to modify the table
model_table_modified <- model_table %>%
  kable() %>%
  kable_styling() %>%
  row_spec(row = which(rownames(model_table) == "treat"), 
           background = "red", color = "white") %>%
  row_spec(which(rownames(model_table) == "treat"), 
           bold = TRUE, italic = TRUE) %>%
  column_spec(column = which(rownames(model_table) == "treat"), 
              background = "red", color = "white")

# Printing the modified table
model_table_modified
```

**Question 3.8**: Write a piece of code that exports this table (without the formatting) to a Word document.

```{r}
library(pander)

# Convert the modified table to a markdown table
markdown_table <- pandoc.table(model_table_modified)

# Write the markdown table to a Word document
writeLines(markdown_table, "model_summary.doc")

```

## The End
